Is high social class always beneficial for survival? Social inequality in mortality

### 2017-08-21 article.Rmd

---
title: Is high social class always beneficial for survival? Social inequality in mortality
  among adults and elderly in Northern Sweden 1851--2013
author: "Sören Edvinsson and Göran Broström"
date: "`r Sys.Date()`"
documentclass: article
citation-package: natbib
bibliography: "mybib.bib"
biblio-style: "apalike"
output:
  bookdown::pdf_document2:
    number_sections: yes
    toc: yes
    toc_depth: 2
  bookdown::html_document2:
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
  bookdown::word_document2:
    toc: yes
    toc_depth: 2
    toc_float: yes
---

>>>>

---
title: Is high social class always beneficial for survival? Social inequality in mortality
  among adults and elderly in Northern Sweden 1851--2013
author: "Sören Edvinsson and Göran Broström"
date: "`r Sys.Date()`"
documentclass: article
citation-package: natbib
bibliography: "mybib.bib"
biblio-style: "apalike"
output:
  bookdown::html_document2:
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
  bookdown::pdf_document2:
    number_sections: yes
    toc: yes
    toc_depth: 2
  bookdown::word_document2:
    toc: yes
    toc_depth: 2
    toc_float: yes
---
